Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-23 paper/supplemental/cremi.tex
Ready for submission.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset (split error correction only). All measurements are reported as median VI, the lower the better. The threshold for automatic selection is $p_t=0.95$ (red line). The slope of the selection oracle shows that guided proofreading reduces VI faster.}
\label{fig:cremiAtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset (only split error correction). Lower VI scores are better. Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.}
\label{fig:cremiCtrails}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiAtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on 5 sections of the CREMI A dataset. All measurements are reported as median VI, the lower the better. The threshold for automatic selection is $p_t=0.95$ (red line). The slope of the selection oracle shows that guided proofreading reduces VI faster.}
\label{fig:cremiAtrails}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremiCtrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the CREMI C dataset. Lower VI scores are better. Guided proofreading corrects the initial segmentation faster with less corrections than focused proofreading.}
\label{fig:cremiCtrails}
\end{figure}
